Viscous Transport in Eroding Porous Media

### 2019-06-10 docs/transport/erosion_transport.tex
do the result section in transport paper

In Fig.~\ref{fig:Eroding20area} and Fig.~\ref{fig:Eroding20flowrate} we
measure the area occupied by bodies and the flow rate $U$ quantifily
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid.

The flow rate increases exponentially with growth rate close to
$\ln10^4$.

@@

In Fig.~\ref{fig:Eroding20tort}(c)
In Fig.~\ref{fig:Eroding20tort}(d) 
}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of U verse time.}
\end{figure}

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tortU_local}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
\end{figure}

>>>>

In Fig.~\ref{fig:Eroding20area} we
measure the area occupied by bodies 
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
all the bodies are vanished completely.

Fig.~\ref{fig:Eroding20flowrate} we record the flow rate $U$ quantifily
during the eroding. Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area occupied by bodies is getting smaller $U$ is getting larger.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
with growth rate close to $\ln10^4$.

@@

In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
and draw 
In Fig.~\ref{fig:Eroding20tort}(d) 
}

@@

\begin{figure}[H]
%\begin{subfigure}[b]{0.5\textwidth}
\center
\includegraphics*[width =0.5\linewidth]{./figs/flow_rate20dense}
%\caption{}
%\end{subfigure}%
%\begin{subfigure}[b]{0.5\textwidth}
%\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
%\caption{}
%\end{subfigure}
\caption{\label{fig:Eroding20flowrate}  The incoming flow rate of U verse time.}
\end{figure}

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top20}
\caption{\label{fig:Eroding20tort_traj} The largest 20 difference of the length of 
two neighbor tracers' trajectories in
 20 nearly touching bodies eroding}
\end{figure}
